The Anthropological Notation Ontology (ANNO): A core ontology for annotating human bones and deriving phenotypes

### 2023-07-31 paper.tex
indicate equal contribution

% For one author:
%\author{\inits{N.}\fnms{Name1} \snm{Surname1}\ead[label=e1]{first@somewhere.com}}
%\address{Department first, \orgname{University or Company name},
%Abbreviate US states, \cny{Country}\printead[presep={\\}]{e1}}
% Höffner, Heuschkel, Schmiedel, Penne, Fritzsch, Ludwig, Mohaupt, Labudde, Uciteli
% TODO: overleaf
% Two or more authors:
\begin{aug}
\author[B]{\inits{M.}\fnms{Marie} \snm{Heuschkel}\ead[label=e2]{marie.heuschkel@hs-mittweida.de}}
\author[A]{\inits{K.}\fnms{Konrad} \snm{Höffner}\ead[label=e1]{konrad.hoeffner@uni-leipzig.de}%
\thanks{Corresponding author. \printead{e1}.}
\thanks{Equal contribution.}%how to show this for the first 3?
}
\author[B]{\inits{F.}\fnms{Fabian} \snm{Schmiedel}\ead[label=e3]{fabian.schmiedel@hs-mittweida.de}}
\author[B]{\inits{D.}\fnms{Dirk} \snm{Labudde}\ead[label=e10]{dirk.labudde@hs-mittweida.de }}
\author[A]{\inits{A.}\fnms{Alexandr} \snm{Uciteli}\ead[label=e11]{alexander.uciteli@imise.uni-leipzig.de}}
%\author[B]{\inits{}\fnms{} \snm{}\ead[label=e9]{}}
\address[A]{Institute for Medical Informatics, Statistics and Epidemiology (IMISE), \orgname{Leipzig University},
Saxony, \cny{Germany}\printead[presep={\\}]{e1,e11}}
\address[B]{\orgname{Hochschule Mittweida},
Saxony, \cny{Germany}\printead[presep={\\}]{e2,e3,e10}}
\end{aug}

>>>>

% For one author:
%\author{\inits{N.}\fnms{Name1} \snm{Surname1}\ead[label=e1]{first@somewhere.com}}
%\address{Department first, \orgname{University or Company name},
%Abbreviate US states, \cny{Country}\printead[presep={\\}]{e1}}
% Höffner, Heuschkel, Schmiedel, Penne, Fritzsch, Ludwig, Mohaupt, Labudde, Uciteli
% TODO: overleaf
% Two or more authors:
\begin{aug}
\author[B,C]{\inits{M.}\fnms{Marie} \snm{Heuschkel}\ead[label=e2]{marie.heuschkel@hs-mittweida.de}}
\author[A,C]{\inits{K.}\fnms{Konrad} \snm{Höffner}\ead[label=e1]{konrad.hoeffner@uni-leipzig.de}%
\thanks{Corresponding author. \printead{e1}.}
}
\author[B,C]{\inits{F.}\fnms{Fabian} \snm{Schmiedel}\ead[label=e3]{fabian.schmiedel@hs-mittweida.de}}
\author[B]{\inits{D.}\fnms{Dirk} \snm{Labudde}\ead[label=e10]{dirk.labudde@hs-mittweida.de }}
\author[A]{\inits{A.}\fnms{Alexandr} \snm{Uciteli}\ead[label=e11]{alexander.uciteli@imise.uni-leipzig.de}}
\address[A]{Institute for Medical Informatics, Statistics and Epidemiology (IMISE), \orgname{Leipzig University},
Saxony, \cny{Germany}\printead[presep={\\}]{e1,e11}}
\address[B]{\orgname{Hochschule Mittweida},
Saxony, \cny{Germany}\printead[presep={\\}]{e2,e3,e10}}
\address[C]{equal contribution}
\end{aug}
